Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-18 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Updated FDS refs, comment fixes

\chapter{Summary of Experimental Results}

Needed?

{}
\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}

In this chapter the application of empirical algebraic fire characterizations will be examined. Two different types of applications will be used.  In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.  In the second case, the height of the thermal damage on the gypsum board will be examined. Applications of algorithms such as these are presented in current fire investigation textbooks~\cite{Icove:2013}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/PointSourceHF}
	\caption{Schematic of heat flux estimation using the point source assumption}
	\label{PointSourceHF}
\end{figure}

>>>>

\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}

Over the years, fire researchers have provided many methods for predicting flame characteristics such as: median flame height, plume temperatures and an estimation of the heat flux emitted. These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,FDS_Users_Guide},FDS_Tech_Guide}

In this chapter the application of empirical algebraic flame characterizations will be compared against the results from the experiments documented in Chapter 2 and 4. Two different types of applications will be used.  In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.  In the second case, the height of the thermal damage on the gypsum board will be examined. Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999}}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/PointSourceHF}
	\caption{Schematic of heat flux estimation using the point source assumption}
	\label{PointSourceHF},
\end{figure},
